Variance in scarid grazing behavior across Caribbean reef sites

### 2019-12-06 r/Paper_analyses.Rmd
grazing intensity + pca loadings

---
title: "Variance in scarid grazing behavior across Caribbean reef sites"
author: "Molly Wilson"
date: "3/1/2019"
output: html_document
---

# Variance in scarid grazing behavior across Caribbean reef sites
### Formatted as: Coral Reefs note (<2900 words)

```{r, echo=F, message=F, warning=F}
library(here)
library(tidyverse)
library(R.utils)
library(ggplot2)
library(gridExtra)
library(grid)
library(ggfortify)
library(ggsignif) # boxplot stats
library(EnvStats) # boxplot stats
library(mgcv)
library(MuMIn)
library(knitr)
library(factoextra)

site <- read.csv(here("data", "site.csv"), strip.white = T, stringsAsFactors = F) %>% select(-X)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  filter(phase == "i" & 
           species_code %in% c("stop","qup") & 
           length_cm <= 30 & length_cm >= 15 & 
           !(species_code == "stop" & site == "Pallaster West") & 
           !(species_code == "qup" & site %in% c("Pallaster East","Rendezvous","Turtle Bay"))) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island) %>%
  filter(fr <= 3000)

sum_ssp_sub <- sum_id %>% 
  group_by(species, species_code, site, island) %>%
  summarize(
    n=n(),
    length_median=median(length_cm),
    length_se=sd(length_cm)/sqrt(n),
    g_frac_median=median(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_median=median(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_median=median(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n)
    ) %>%
  left_join(site, by = c("island","site"))

@@

## Sample sizes (Table S1)
```{r}
sample <- sum_id %>%
  group_by(island, site, species) %>% 
  summarize(n=n()) %>%
  arrange(island) %>%
  rename_all(capitalize)
kable(sample)
write.csv(sample, file = here("figs/sample.csv"))

@@

## Table 1. Variable definitions
```{r, echo=F, message=F}
Variable <- c('Time spent grazing','Bite rate','Feeding rate','Foray size')
Definition <- c('Proportion of time spent grazing during follow','Bite rate while actively Grazing','Bite rate over total follow time','Number of consecutive bites taken during single grazing foray')
Unit <- c('fraction','bites/second','bites/minute','bites/foray')
var.table <- data.frame(Variable,Definition,Unit)
kable(var.table)
```

## Testing parametric assumptions
```{r}
### Normality

hist(sum_id$fr) # positive skew
shapiro.test(sum_id$fr) # non-normal

@@

# all positively skewed, non-normally distributed -> should use median, should use Kruskall-Wallis
```

## Panel graph of site differences
```{r, echo = F, message = F, warning = F}
# published Feeding rate (bites/min) for reference lines if needed
ref_qup15 <- (3329-33*15)/60
ref_qup30 <- (3329-33*30)/60
ref_stop15 <- (1089-17*15-56)/60
ref_stop30 <- (1089-17*30-56)/60

@@

legend_plot <- 
  ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "") +
  theme_bw() +
  theme(legend.position = "right",
        legend.title = element_blank())

@@

g <- arrangeGrob(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1,1,1,1.5)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))

@@

## Kruskal-Wallis tests
```{r}
vir <- sum_id %>% filter(species_code == "stop")
vet <- sum_id %>% filter(species_code == "qup")

kruskal.test(fr ~ site, data = vet) # p<0.001
kruskal.test(fr ~ site, data = vir) # p<0.001

kruskal.test(br ~ site, data = vet) # p>0.5 (p=0.63)
kruskal.test(br ~ site, data = vir) # p>0.5 (p=0.55)

kruskal.test(g_frac ~ site, data = vet) # p<0.001
kruskal.test(g_frac ~ site, data = vir) # p<0.001

kruskal.test(for_bites ~ site, data = vet) # p<0.001
kruskal.test(for_bites ~ site, data = vir) # p<0.001
```

@@

```{r, echo=F, message=F, warning=F}
fr_q1 <- ggplot(filter(sum_ssp_sub, species_code == "qup"), aes(x = scar_bm/1000, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "",
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 1, 0, 0, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

@@

```{r, eval = F, echo = F, message=F, warning=F}
# grazing impact (vg ~ volume grazed) of fish from behavioral surveys
sum_id_vg <- sum_id %>%
  filter(species_code != "rbp") %>%
  mutate(
    bs = ifelse(species_code == "stop", 5.257*10^-4*length_cm^2, 4.013*10^-4*length_cm^2), # adding bite size equations from Mumby
    bh_capped = ifelse(ta_canopy < 2*sqrt(bs)/(22/7), ta_canopy, 2*sqrt(bs)/(22/7)), # if ta_canopy exceeds diameter of bite size, bite height is capped at bite size
    bv = bs*ta_canopy,
    bv_capped = bs*bh_capped,
    vg = fr*bv,
    vg_capped = fr*bv_capped,
    island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))
) %>%
  arrange(island)

# summing by site, species, and phase
sum_ssp_vg <- sum_id_vg %>% 
  filter(length_cm >= 15 & length_cm <= 30) %>%
  group_by(site, ta_canopy, island, species, species_code, phase) %>% 
  summarize(
    n=n(),
    vg_median=median(vg),
    vg_se=sd(vg)/sqrt(n),
    vg_capped_median=median(vg_capped),
    vg_capped_se=sd(vg_capped)/sqrt(n),
    fr_median=median(fr)
    ) %>% 
  select(-n)

# keep this to get legend for panel
vg_facet <- ggplot(filter(sum_ssp_vg, species_code != "rbp" & phase == "i"), aes(x=factor(site, levels = sum_site$site), y=vg_median)) +
    geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
    geom_errorbar(aes(ymin=vg_median-vg_se, ymax=vg_median+vg_se), width=.2,
                 position=position_dodge(.9)) +
    facet_grid(~species) +
    scale_fill_brewer(palette = "Blues") +
    labs(title="median grazing impact by volume (initial phase)", 
         y="Grazing impact (cm3/hr)", 
         x="Site") +
    theme_bw() +
    theme(strip.text = element_text(face = "italic"), 
          axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.title = element_blank())

vg_qup <- ggplot(filter(sum_ssp_vg, species_code == "qup" & phase == "i"), 
                 aes(x=factor(site, levels = sum_site$site), y=vg_median)) +
    geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
    geom_errorbar(aes(ymin=vg_median-vg_se, ymax=vg_median+vg_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = expression('Grazing impact (cm'^3*'/hr)'), 
       x = "", 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.margin = margin(1, 0, 0, 5, unit = "pt"),
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, face = "italic")
        )

vg_stop <- ggplot(filter(sum_ssp_vg, species_code == "stop" & phase == "i"), 
                  aes(x=factor(site, levels = sum_site$site), y=vg_median)) +
    geom_bar(stat = "identity", aes(fill = island), position = "dodge") +    
    geom_errorbar(aes(ymin=vg_median-vg_se, ymax=vg_median+vg_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "S. viride") +
  theme_bw() + 
  theme(plot.margin = margin(1, 1, 0, 0, unit = "pt"),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, face = "italic")
        )

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
  }
legend <- get_legend(vg_facet)

g <- grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))

ggsave(here("figs/bc_bar_panel.png"),g)
```

## PCA
```{r, echo=F, message=F, warning=F}
pca_pred <- prcomp(na.omit(site %>%
                remove_rownames %>% column_to_rownames(var="site") %>%
                select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, scar_den, scar_bm, carn30_bm, lc_cover)),
  center = T, scale = T)

autoplot(pca_pred, data = site, shape = 'island', colour = 'island',
         label = T,
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_manual(values = c("cadetblue3","cadetblue3","cadetblue3")) +
    theme_bw() +
    theme(legend.title = element_blank())
ggsave(here("figs/pca_pred.png"), width = 8, height = 5)

sum_id_pca <- sum_id %>% 
  left_join(select(sum_site,site,pc1_all,pc2_all), by = "site")
sum_ssp_pca <- sum_ssp_sub %>%
  left_join(select(sum_site,site,pc1_all,pc2_all), by = "site")
```

### Better PCA?
```{r, echo=F, message=F, warning=F}
pca_data <- na.omit(site %>%
  select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, lc_cover, scar_bm, scar_den, carn30_bm))
names(pca_data)[1:9] =
  c("rugosity", "macroalgal cover", "macroalgal canopy", "turf cover", "turf canopy", "coral cover", "scarid biomass", "scarid density", "predator biomass")

pca_pred <- prcomp(pca_data, center = T, scale = T)

fviz_pca_biplot(pca_pred,
                col.ind = site$island,
                mean.point = F,
                label = "var",
                repel = T
                ) +
  scale_shape_manual(values=c(15,16,17)) +
  scale_color_manual(values = c("black","black","black")) +
  labs(x = "PC1 (55.6%)", y = "PC2 (24.5%)", title = "") +
  theme_bw() +
  theme(legend.title = element_blank())

ggsave(here("figs/pca_pred.png"), width = 7, height = 5)

@@

Predicting feeding rate (site-level medians, island as random effect)
```{r, echo=F, message=F, warning=F}
m_data <- sum_ssp_pca

@@

# gamm4 <- gamm(fr_median ~ species_code + s(length_mean, by = factor(species_code), k=3) + s(pc1_all, by = factor(species_code), k=3) + s(pc2_all, k=3), 
#            family = gaussian(link=identity),
#            random = list(island=~1),
#            data = m_data
#            )
# g4 <- c("g4", "Species + Size~Species + PC1~Species + PC2", AICc(gamm4$lme), summary(gamm4$gam)$r.sq)

# gamm5 <- gamm(fr_median ~ species + s(length_mean, by = factor(species_code), k=3) + s(pc1_all, by = factor(species_code), k=3), 
#            family = gaussian(link=identity),
#            random = list(island=~1),
#            data = m_data
#            )
# g5 <- c("g5", "Species + Size~Species + PC1~Species", AICc(gamm5$lme), summary(gamm5$gam)$r.sq)

@@

gtab_fr_site <- as.data.frame(rbind(g1,g2,g4,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)

# summary + plots from best models
summary(gamm12$gam)
plot(gamm12$gam,pages=1)
```

Predicting Grazing intensity (site-level medians, island as random effect)
```{r, echo=F, message=F, warning=F}
m_data <- sum_ssp_pca

@@

gamm4 <- gamm(for_bites_median ~ species_code + s(length_mean, by = factor(species_code), k=3) + s(pc1_all, by = factor(species_code), k=3) + s(pc2_all, k=3), 
           family = gaussian(link=identity),
           random = list(island=~1),
           data = m_data
           )
g4 <- c("g4", "Species + Size~Species + PC1~Species + PC2", AICc(gamm4$lme), summary(gamm4$gam)$r.sq)

@@

gtab_fi_site <- as.data.frame(rbind(g1,g2,g3,g4,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)

@@

# Supplement

@@

### loess plots for additional drivers?

>>>>

---
title: 'Variance in scarid grazing behavior across Caribbean reef sites'
author: "*Compiled on `r date()` by Molly Wilson*"
output: 
  html_document:
    toc: true
    code_folding: hide
    number_sections: false
    theme: cerulean
    highlight: haddock

---

*Formatted as: Coral Reefs note*

```{r, message=F, warning=F}
library(here)
library(tidyverse)
library(R.utils)
library(ggplot2)
library(gridExtra)
library(grid)
library(ggfortify)
library(mgcv)
library(MuMIn)
library(knitr)
library(factoextra)

sum_site <- read.csv(here("data", "site.csv"), strip.white = T, stringsAsFactors = F) %>% select(-X)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  filter(phase == "i" & 
           species_code %in% c("stop","qup") &
           ### size subset 15 - 30cm
           length_cm <= 30 & length_cm >= 15 &
           ### excluding sites with less than 7 observations within size subset range
           !(species_code == "stop" & site == "Pallaster West") & 
           !(species_code == "qup" & site %in% c("Pallaster East","Rendezvous","Turtle Bay"))) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island) %>%
  filter(fr <= 3000)

sum_ssp_sub <- sum_id %>% 
  group_by(species, species_code, site, island) %>%
  summarize(
    n=n(),
    length_mean=mean(length_cm),
    length_median=median(length_cm),
    length_se=sd(length_cm)/sqrt(n),
    g_frac_median=median(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_median=median(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_median=median(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n)
    ) %>%
  left_join(sum_site, by = c("island","site"))

@@

## Preliminary investigations

### Sample sizes by site and species
Currently omitting sites with fewer than 7 observations that fall within 15-30cm size subset
```{r, message=F}
sample <- sum_id %>%
  group_by(island, site, species) %>% 
  summarize(n=n()) %>%
  arrange(island) %>%
  rename_all(capitalize)
kable(sample)
write.csv(sample, file = here("figs/sample.csv"))

@@

### Variable definitions
```{r, echo=F, message=F}
Variable <- c('Time spent grazing','Bite rate','Feeding rate','Foray size')
Definition <- c('Proportion of time spent grazing during follow','Bite rate while actively Grazing','Bite rate over total follow time','Number of consecutive bites taken during single grazing foray')
Unit <- c('fraction','bites/second','bites/minute','bites/foray')
var.table <- data.frame(Variable,Definition,Unit)
kable(var.table)
```

### Testing parametric assumptions
Testing for heteroscedasticity first
```{r, message=F}
hist(sum_id$fr) # positive skew
shapiro.test(sum_id$fr) # non-normal

@@

# all positively skewed, non-normally distributed -> should use median, should use Kruskall-Wallis
```
All behavioral variables are positively skewed, non-normally distributed -> should use median values and Kruskall-Wallis instead of ANOVA for site-level differences

## Inter-site differences

Panel graph of behavioral variables across sites:

```{r, message = F, warning = F}
# published Feeding rate (bites/min) for reference lines if needed
ref_qup15 <- (3329-33*15)/60
ref_qup30 <- (3329-33*30)/60
ref_stop15 <- (1089-17*15-56)/60
ref_stop30 <- (1089-17*30-56)/60

@@

legend_plot <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "") +
  theme_bw() +
  theme(legend.position = "right",
        legend.title = element_blank())

@@

g <- arrangeGrob(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1,1,1,2)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))
plot(g)

@@

Kruskal-Wallis tests to look at significance of inter-site variance for different behavioral variables:

Feeding rate:
```{r}
vir <- sum_id %>% filter(species_code == "stop")
vet <- sum_id %>% filter(species_code == "qup")

kruskal.test(fr ~ site, data = vet) # p<0.001
kruskal.test(fr ~ site, data = vir) # p<0.001
```

Bite rate:
```{r}
kruskal.test(br ~ site, data = vet) # p>0.5 (p=0.63)
kruskal.test(br ~ site, data = vir) # p>0.5 (p=0.55)
```

Fraction of time grazing:
```{r}
kruskal.test(g_frac ~ site, data = vet) # p<0.001
kruskal.test(g_frac ~ site, data = vir) # p<0.001
```

Grazing intensity:
```{r}
kruskal.test(for_bites ~ site, data = vet) # p<0.001
kruskal.test(for_bites ~ site, data = vir) # p<0.001
```

All significant (p < 0.001) except for fraction of time spent grazing.

@@

```{r, message=F, warning=F}
fr_q1 <- ggplot(filter(sum_ssp_sub, species_code == "qup"), aes(x = scar_bm/1000, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "",
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 1, 0, 0, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

@@

## PCA

```{r, message=F, warning=F}
pca_data <- na.omit(sum_site %>%
  select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, lc_cover, scar_bm, scar_den, carn30_bm))
names(pca_data)[1:9] =
  c("rugosity", "macroalgal cover", "macroalgal canopy", "turf cover", "turf canopy", "coral cover", "scarid biomass", "scarid density", "predator biomass")

pca_pred <- prcomp(pca_data, center = T, scale = T)
print(pca_pred)
pca_var <- get_pca_var(pca_pred)
print(pca_var$contrib)

fviz_pca_biplot(pca_pred,
                col.ind = sum_site$island,
                mean.point = F,
                label = "var",
                repel = T
                ) +
  scale_shape_manual(values=c(15,16,17)) +
  scale_color_manual(values = c("black","black","black")) +
  labs(x = "PC1 (55.6%)", y = "PC2 (24.5%)", title = "") +
  theme_bw() +
  theme(legend.title = element_blank())

ggsave(here("figs/pca_pred.png"), width = 7, height = 5)
```

```{r, message=F}
sum_site_pca <- sum_site %>% 
  bind_cols(as.data.frame(pca_pred$x) %>% 
           select(PC1,PC2)) %>%
  rename(pc1_all=PC1,
         pc2_all=PC2)

sum_id_pca <- sum_id %>% 
  left_join(select(sum_site_pca,site,pc1_all,pc2_all), by = "site")
sum_ssp_pca <- sum_ssp_sub %>%
  left_join(select(sum_site_pca,site,pc1_all,pc2_all), by = "site")
```

@@

Note that these GAMMs are using the size subsetted data, as opposed to the full size ranges

Predicting feeding rate (site-level medians, island as random effect)
```{r, message=F, warning=F}
m_data <- sum_ssp_pca

@@

gamm4 <- gamm(fr_median ~ species_code + s(length_mean, by = factor(species_code), k=3) + s(pc1_all, by = factor(species_code), k=3) + s(pc2_all, k=3),
           family = gaussian(link=identity),
           random = list(island=~1),
           data = m_data
           )
g4 <- c("g4", "Species + Size~Species + PC1~Species + PC2", AICc(gamm4$lme), summary(gamm4$gam)$r.sq)

gamm5 <- gamm(fr_median ~ species + s(length_mean, by = factor(species_code), k=3) + s(pc1_all, by = factor(species_code), k=3),
           family = gaussian(link=identity),
           random = list(island=~1),
           data = m_data
           )
g5 <- c("g5", "Species + Size~Species + PC1~Species", AICc(gamm5$lme), summary(gamm5$gam)$r.sq)

@@

gtab_fr_site <- as.data.frame(rbind(g1,g2,g3,g4,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)
kable(gtab_fr_site)

# summary + plots from best models
summary(gamm10$gam)
plot(gamm10$gam,pages=1)
```

Predicting grazing intensity (site-level medians, island as random effect)
```{r, echo=F, message=F, warning=F}
m_data <- sum_ssp_pca

@@

# gamm4 <- gamm(for_bites_median ~ species_code + s(length_mean, by = factor(species_code), k=3) + s(pc1_all, by = factor(species_code), k=3) + s(pc2_all, k=3),
#            family = gaussian(link=identity),
#            random = list(island=~1),
#            data = m_data
#            )
# g4 <- c("g4", "Species + Size~Species + PC1~Species + PC2", AICc(gamm4$lme), summary(gamm4$gam)$r.sq)

@@

gtab_fi_site <- as.data.frame(rbind(g1,g2,g3,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)
kable(gtab_fr_site)

@@

## Supplement/optional

@@

### Loess plots for additional drivers?
